\section{Evaluation Metrics}

To assess the impact of GEO strategies systematically, we introduce five evaluation metrics designed to quantify visibility readiness across semantic, structural, and generative dimensions. Each metric is defined with a clear threshold and justification.

\subsection{AIO Semantic Focus Score}
\textbf{Definition:} Proportion of sentences that directly support the declared topic.
\begin{equation}
\text{AIO}_{T} = \frac{\text{Number of topic-relevant sentences}}{\text{Total number of sentences}}
\end{equation}
\textbf{Threshold:} $> 0.75$

\subsection{Citation Potential Score}
\textbf{Definition:} Composite score measuring factuality, authority, practical utility, and presentation.
\begin{equation}
\text{CPS} = \frac{1}{4}\sum_{i=1}^{4} \text{score}_i
\end{equation}
\textbf{Sources:} Scores derived from G-Eval-style rubric \cite{liu2023verifiability, menick2022quotes}.
\textbf{Threshold:} $> 0.70$

\subsection{Structural Readiness Score}
\textbf{Definition:} Ratio of actual to expected Schema.org types deployed correctly.
\begin{equation}
\text{SRS} = \frac{\text{Valid schemas used}}{\text{Expected schemas}}
\end{equation}
\textbf{Schemas:} \texttt{Article}, \texttt{FAQPage}, \texttt{Person}, etc.
\textbf{Threshold:} $> 0.80$

\subsection{Modular Extractability Score}
\textbf{Definition:} Ratio of extractable blocks (FAQs, lists, modular paragraphs) to total content blocks.
\begin{equation}
\text{MES} = \frac{\text{Extractable units}}{\text{Paragraphs + Lists}}
\end{equation}
\textbf{Threshold:} $> 0.65$

\subsection{Multi-Modal Adaptability Score}
\textbf{Definition:} Presence of captions, tables, figure descriptions, or podcast/video-ready outlines.
\begin{equation}
\text{MMAS} = \frac{\text{Alternate format sections}}{\text{Total sections}}
\end{equation}
\textbf{Threshold:} $> 0.60$

These metrics align with and expand on the visibility functions and impression metrics introduced in GEO-Bench \cite{aggarwal2024geo}. They also support reproducible benchmarking across domains and platforms.
